Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-09-07 CCPE/Mauscript/sec3-experiment-design.tex
update

\paragraph{Hyper-parameters}
We use $dim(\boldsymbol{v})$ to denote the dimension of a vector $\boldsymbol{v}$.
We picked the hyper-parameters of GNNs according to their popularity in the original papers.
We used the same set of hyper-parameters for all the datasets. 
Some hyper-parameters like the dimensions of hidden feature vectors were common in the four GNNs and we set them to the same values.
For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)=\#Classes$.
For GAT, we set the hyper-parameters according to \cite{huang2018_gat}.
The first GAT layer had 8 heads with the dimension of each head $d^0_{head}=8$. The first GAT layer merged the heads by concatenating.
The second GAT layer used a single head with the dimension $d^1_{head}=d^1_{out}=\#Classes$.
For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_i) = dim(\boldsymbol{h}^1_i) = dim(\boldsymbol{h}^2_i) = 64$.
We used 8 heads in the both GaAN layers with $d_a=d_v=8$ and $d_m=64$.

@@

We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques respectively.
For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1, and 10 for GNN Layer 0 and set the default batch size as 512 from \cite{hamilton2017_graphsage}.
For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to \cite{chiang2019_cluster_gcn}.

>>>>

\paragraph{Hyper-parameters}
We use $dim(\boldsymbol{v})$ to denote the dimension of a vector $\boldsymbol{v}$.
We picked the hyper-parameters of GNNs according to their popularity in the original papers.
We used the same set of hyper-parameters for all the datasets. 
Some hyper-parameters like the dimensions of hidden feature vectors were common in the four GNNs and we set them to the same values.
For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)=\#Classes$.
For GAT, we set the hyper-parameters according to its paper\cite{huang2018_gat}.
The first GAT layer had 8 heads with the dimension of each head $d^0_{head}=8$. The first GAT layer merged the heads by concatenating.
The second GAT layer used a single head with the dimension $d^1_{head}=d^1_{out}=\#Classes$.
For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_i) = dim(\boldsymbol{h}^1_i) = dim(\boldsymbol{h}^2_i) = 64$.
We used 8 heads in the both GaAN layers with $d_a=d_v=8$ and $d_m=64$.

@@

We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques respectively.
For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1, and 10 for GNN Layer 0 and set the default batch size as 512 from its paper\cite{hamilton2017_graphsage}.
For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to the parameters used in its paper\cite{chiang2019_cluster_gcn}.
